### 2018-07-05 paper/6-engineering.tex
S6

In our model we define a \hs{Task} as a function -- when given the same inputs
it will always produce the same output. Alas, the real-world is not so obliging.
Some examples of impure tasks include:

@@

For examples like \LaTeX~we consider the proper encoding to not be with circular
tasks, but with a series of iterative steps, as described
by~\citet{shake-fixed-point}. It is important that the number of executions is
bounded, otherwise the build system may not terminate (a legitimate concern
with \LaTeX, which can be put into a situation where it is bistable or diverging
over multiple executions). The examples in \Excel tend to encode either mutable
state, or recurrence relations. The former is only required because \Excel
inherently lacks the ability to write mutable state, and the latter is probably
better solved using explicit recurrence formulae.

>>>>

In our model we define \hs{Task} as a function -- when given the same inputs
it will always produce the same output. Alas, the real-world is not so obliging.
Some examples of impure tasks include:

@@

For examples like \LaTeX~we consider the proper encoding to not be circular
tasks, but a series of iterative steps, as described
by~\citet{shake-fixed-point}. It is important that the number of executions is
bounded, otherwise the build system may not terminate (a legitimate concern
with \LaTeX, which can be put into a situation where it is bistable or diverging
over multiple executions). The examples in \Excel tend to encode either mutable
state, or recurrence relations. The former is only required because \Excel
inherently lacks the ability to write mutable state, and the latter is probably
better solved using explicit recurrence formulae.
